Gradual Soundness: Lessons from Static Python

### 2022-01-13 pj-7.1/paper.tex
pj: abstract / sec 1, mention property-based tests

  \paragraph{Knowledge}
  % What new facts were uncovered? If the
  % research was not results oriented, what new
  % capabilities are enabled by the work?
  Our main finding is that the \emph{gradual soundness}\/ that
  arises from a mix of concrete and transient types is an effective
  way to lower the maintenance cost of the concrete approach.
  We also find that method-based JIT technology can eliminate the
  costs of the transient approach.
  On a more technical level, this paper contributes two artifacts:
  a model of \SP{} that passes hundreds of tests from the \SP{} codebase,
  and a performance evaluation of \SP{}. The process of formalization
  found several errors in the implementation, including fatal errors.

@@

  \paragraph{Grounding}
  % What argument, feasibility proof, artifacts,
  % or results and evaluation support this work?
  Our model of \SP{} is implemented in PLT Redex and tested against
  the \SP{} regression suite.
  This paper includes a small core of the model to convey the main ideas
  of the \SP{} approach and its soundness.
  Our performance claims are based on production experience in the Instagram
  web server.
  Thanks to \SP{}, global CPU usage has improved by almost 4\% within a year.

@@

  \item
    \emph{Mechanization}.
    To validate the soundness of \SP{}, we mechanized a core language in PLT Redex
    and ran over 200 tests adapted from the \SP{} regression suite.
    The model brings across the essence of \SP{} and lends support to the claim
    that core \SP{} is indeed sound.
    Perhaps more importantly, the \emph{process} of modeling revealed 20 significant
    issues in \SP{}.
    Four of these were critical soundness bugs.

>>>>

  \paragraph{Knowledge}
  % What new facts were uncovered? If the
  % research was not results oriented, what new
  % capabilities are enabled by the work?
  Our main finding is that the \emph{gradual soundness}\/ that
  arises from a mix of concrete and transient types is an effective
  way to lower the maintenance cost of the concrete approach.
  We also find that method-based JIT technology can eliminate the
  costs of the transient approach.
  On a more technical level, this paper contributes two artifacts:
  a model of \SP{} that passes property-based tests and hundreds of tests from the \SP{} codebase,
  and a performance evaluation of \SP{}. The process of formalization
  found several errors in the implementation, including fatal errors.

@@

  \paragraph{Grounding}
  % What argument, feasibility proof, artifacts,
  % or results and evaluation support this work?
  Our model of \SP{} is implemented in PLT Redex and tested using
  property-based soundness tests and the \SP{} regression suite.
  This paper includes a small core of the model to convey the main ideas
  of the \SP{} approach and its soundness.
  Our performance claims are based on production experience in the Instagram
  web server.
  Thanks to \SP{}, global CPU usage has improved by almost 4\% within a year.

@@

  \item
    \emph{Mechanization}.
    To validate the soundness of \SP{}, we mechanized a core language in PLT Redex
    and ran both property-based soundness tests and over 200 tests adapted from the \SP{} regression suite.
    The model brings across the essence of \SP{} and lends support to the claim
    that core \SP{} is indeed sound.
    Perhaps more importantly, the \emph{process} of modeling revealed 20 significant
    issues in \SP{}.
    Four of these were critical soundness bugs.
